---
title: "Amazon RO Analytics"
author: "Elias Murcray"
date: "2023-11-11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Collection

Data was collected via survey on the Amazon Interns and New Grads Discord server. There was an original survey that involved manual entry, which was later merged with the new dataset from Google Forms.


```{r}
data = read.csv("./Amazon RO Analytics - Responses.csv")
```

## Data Cleaning

Due to the nature of merging two fragmented datasets, we need to clean the data.


```{r}
# Remove Data From Original Form
data <- subset(data, data$Timestamp != "" & !is.na(data$Timestamp))
# Trim trailing spaces in status from first input
data$Status <- trimws(data$Status)
# Remove participant if no portal specified
data <- subset(data, data$Portal != "" & !is.na(data$Portal))
# Clean orgs
data$Organization = trimws(tolower(data$Organization))
# Remove the people putting just "AWS"
data <- subset(data, data$Organization != "aws")
```

## Offer Frequency

### Based on Portal

```{r}
table(data$Status, data$Portal)
```
### Between Orgs

```{r}
table(data$Organization, data$Status)
```

## Offers

### Full Time Offers In ASP

```{r}
subset(data, (Status %in% c("Offer", "Portal Update")) & Seeking == "Full time" & Portal == "ASP")
```

### Full Time Offers in ECT

```{r}
subset(data, Status == "Offer" & Seeking == "Full time" & Portal == "ECT")
```

### Intern Offers in ASP

```{r}
subset(data, Status == "Offer" & Seeking == "Internship" & Portal == "ASP")
```

### Intern Offers in ECT

```{r}
subset(data, Status == "Offer" & Seeking == "Internship" & Portal == "ECT")
```

### 2x Intern to FT

```{r}
ft <- subset(data, Seeking == "Full time")
prop.table(table(ft$Intern.Type, ft$Status), margin = 1) * 100
```

## Newsletter

It's fun to speculate.

```{r}
table(data$Status, data$Newsletter)
```

